Dissecting Neural Style Transfer

### 2019-05-26 paper/paper.tex
1

The arrays after the initial image are called feature maps, because their value means
``how much a feature x exists at position y and x''.
For example in a $1\times64\times512\times512$ feature map, it means there are 64 types of features.
and its [1, 17, 111, 222] element, would then refer to the extent that the 17th type feature exists
at the position of the 222th column of the 111th row. This ``extent'' could also be negative.

@@

The style loss $L_\text{content}$ can actually be a sum of several style losses, or sometimes just one.
For each style loss, 
both the current image under optimisation and the style image are passed through the vgg19 model.
The two outputs of a certain function in the model are extracted, 
and converted to Gram matrices. We will elabrate on what Gram matrices are,
for now they are just square matrices computed from multidimensional arrays (i.e. feature maps).
For example, the Gram matrix (in the style transfer algorithm) of a $1\times64\times512\times512$ array
is a $64\times64$ matrix.
The point is to compute something that describe the distributions of features
in the image without the spatial information of where the features are.
Gram matrices describe the distributions with correlation between features.
The several style losses are computed with the outputs of different functions.
Otherwise, each of the several style losses are computed in exactly the same way.
Again outputs of which functions in the model to derive style losses from is really adjustable.
A nice default is \verb|conv_1|,\verb|conv_2|,...,\verb|conv_5|. We illustrate
the style losses derived from the output of \verb|conv_1| in Figure $\ref{styleloss}$.

>>>>

The arrays after the initial image are called feature maps, because their value means
``how much a feature x exists at position y and x''.
Take a $1\times64\times512\times512$ feature map for example. There are 64 types of features.
Its [1, 17, 111, 222] element, would then refer to the extent that the 17th type feature exists
at the position of the 222th column of the 111th row. This ``extent'' could also be negative.

@@

The style loss $L_\text{content}$ can actually be a sum of several style losses, or sometimes just one.
For each style loss, 
both the current image under optimisation and the style image are passed through the vgg19 model.
The two outputs of a certain function in the model are extracted, 
and converted to Gram matrices. We will elabrate on what Gram matrices are later.
For now a Gram matrix is just a square matrix computed from a multidimensional array (i.e. a feature map).
For example, the Gram matrix (in the style transfer algorithm) of a $1\times64\times512\times512$ array
is a $64\times64$ matrix.
The point is to compute something that describe the distributions of features
in the image without the spatial information of where the features are.
Gram matrices describe the distributions with correlation between features.
The several style losses are computed with the outputs of different functions.
Otherwise, each of the several style losses are computed in exactly the same way.
Again outputs of which functions in the model to derive style losses from is really adjustable.
A nice default is \verb|conv_1|,\verb|conv_2|,...,\verb|conv_5|. We illustrate
the style losses derived from the output of \verb|conv_1| in Figure $\ref{styleloss}$.
